---
title: "Guitar take: research report"
subtitle: "Local offline evidence; listening acceptance is separate"
format:
  html:
    embed-resources: false
    toc: true
params:
  run_dir: "../runs/demo"
execute:
  echo: false
  warning: false
  message: false
---

This optional Quarto report consumes the same run exports as the standard-library
`report.html`. It does not establish listening quality, source recovery, intended
meter or performance mistakes.

## Run evidence

```{r}
run_dir <- normalizePath(params$run_dir, mustWork = FALSE)
manifest_path <- file.path(run_dir, "manifest.json")
lineage_code <- paste(
  "import sys; from pathlib import Path;",
  "sys.path.insert(0,str(Path(sys.argv[1]).resolve())); import report;",
  "root=Path(sys.argv[2]).resolve();",
  "print(report.analysis_lineage(root,report.load_json(root/'manifest.json'),report.load_json(root/'analysis.json')))"
)
analysis_lineage <- suppressWarnings(system2(
  "python3", c("-c", shQuote(lineage_code), shQuote("../scripts"), shQuote(run_dir)),
  stdout = TRUE, stderr = FALSE
))
analysis_bound <- length(analysis_lineage) == 1 && analysis_lineage %in%
  c("original_source_hash_bound", "verified_run_derivative_hash_bound")
if (!file.exists(manifest_path)) {
  cat("Run manifest unavailable. Render with the intended run_dir parameter.")
} else if (!requireNamespace("jsonlite", quietly = TRUE)) {
  cat("Manifest exists; jsonlite is unavailable. The local static HTML report remains usable.")
} else {
  manifest <- jsonlite::fromJSON(manifest_path, simplifyVector = FALSE)
  measurements <- manifest$measurements
  if (is.null(measurements)) measurements <- manifest$metrics
  if (is.null(measurements)) measurements <- manifest$loudness
  if (is.null(measurements)) {
    cat("Measurements unavailable in this manifest.")
  } else {
    print(measurements)
  }
}
```

## Timing candidates

```{r}
source("plots.R")
if (analysis_bound) {
  plot_run_events(run_dir)
} else {
  plot.new()
  text(0.5, 0.5, "Source-bound rhythm analysis unavailable or rejected")
}
```

The plot uses decoded-audio-relative seconds. Click and guitar onset candidates
may overlap; detector bias and room propagation delay affect timing. A tempo
candidate is not an accepted beat grid. Missed or extra notes require an approved
expected-rhythm reference.

## Listening review

Open the run directory's `report.html` for manual original/processed/residual
playback and processed video. Compare at matched playback loudness. Listen for
preserved pick attacks, palm-mute articulation, sustained harmonics and natural
tails; inspect the residual for removed musical detail. A mono-mixture residual
is a diagnostic estimate, not a recovered original stem.
