---
title: "Guitar take: research report"
subtitle: "Hash-bound metadata bundle; listening acceptance is separate"
params:
  run_dir: ""
execute:
  echo: false
  warning: false
  message: false
---

This optional Quarto report reads a **metadata-only, hash-bound bundle** built by
`scripts/report_bundle.py`. The `params$run_dir` value is that bundle's absolute
path. The bundle is verified before any value is shown. The plain `report.html`
written by `scripts/report.py` remains the primary report. This document does not
establish listening quality, source recovery, intended meter or performance
mistakes.

```{r setup}
bundle_dir <- if (is.null(params$run_dir)) "" else as.character(params$run_dir)
verifier <- normalizePath(file.path("..", "scripts", "report_bundle.py"), mustWork = FALSE)
run_verifier <- function(extra) {
  out <- tryCatch(
    suppressWarnings(system2("python3", c(shQuote(verifier), "verify", "--bundle-dir", shQuote(bundle_dir), extra),
                             stdout = TRUE, stderr = FALSE)),
    error = function(e) character(0)
  )
  if (!length(out)) "refused:verifier_unavailable" else out
}
status <- if (nzchar(bundle_dir)) tail(run_verifier("--status-only"), 1) else "refused:run_dir_parameter_missing"
verified <- identical(status, "verified")
bundle_sha <- NA_character_
if (verified) {
  detail <- paste(run_verifier(character(0)), collapse = " ")
  found <- regmatches(detail, regexpr("\"bundle_sha256\": \"[0-9a-f]{64}\"", detail))
  if (length(found)) bundle_sha <- sub(".*\"([0-9a-f]{64})\"$", "\\1", found)
}
table_of <- function(name) {
  path <- file.path(bundle_dir, "tables", name)
  if (!verified || !file.exists(path)) return(NULL)
  read.csv(path, stringsAsFactors = FALSE, check.names = FALSE, colClasses = "character", na.strings = character(0))
}
show_table <- function(frame, empty = "Not available in this bundle.") {
  if (is.null(frame) || !nrow(frame)) {
    cat(empty, "\n\n")
  } else if (requireNamespace("knitr", quietly = TRUE)) {
    print(knitr::kable(frame, row.names = FALSE))
    cat("\n\n")
  } else {
    print(frame, row.names = FALSE)
  }
}
prefix <- function(x, n = 12) ifelse(nchar(x) > n, paste0(substr(x, 1, n), "..."), x)
value_of <- function(frame, field) {
  if (is.null(frame)) return(NA_character_)
  hit <- frame$value[frame$field == field]
  if (length(hit)) hit[1] else NA_character_
}
```

```{r status}
#| results: asis
if (verified) {
  cat("Bundle verification: **verified** (every member hash and the bundle hash were recomputed).\n\n")
} else {
  cat("Bundle verification: **", status, "**. No bundle values are shown. ",
      "Rebuild the bundle with `scripts/report_bundle.py build`, or use the plain `report.html`.\n\n", sep = "")
}
```

## 1. Bundle identity

```{r identity}
#| results: asis
identity <- table_of("identity.csv")
if (verified && !is.null(identity)) {
  rows <- data.frame(
    field = c("run_id", "manifest sha256", "source sha256", "bundle sha256", "duration (s)",
              "analysis basis", "analysis run", "analysis lineage", "analysis status"),
    value = c(value_of(identity, "run_id"), prefix(value_of(identity, "manifest_sha256")),
              prefix(value_of(identity, "source_sha256")), prefix(bundle_sha),
              value_of(identity, "duration_seconds"), value_of(identity, "analysis_basis"),
              value_of(identity, "analysis_run_id"), value_of(identity, "analysis_lineage"),
              value_of(identity, "analysis_status")),
    stringsAsFactors = FALSE)
  show_table(rows)
} else {
  cat("Unavailable: the bundle did not verify.\n\n")
}
```

## 2. Stage-file hash verification

Stage files are recorded by name and sha256 only; no audio enters the bundle.

```{r stages}
#| results: asis
stages <- table_of("stage_files.csv")
if (!is.null(stages)) stages$expected_sha256 <- prefix(stages$expected_sha256)
show_table(stages)
auxiliary <- table_of("auxiliary.csv")
cat("Auxiliary payload binding (dag, flags, markers, phrases):\n\n")
show_table(auxiliary)
```

## 3. S2 measured comparisons (quoted from receipts)

Each figure is the named receipt's own measurement or label, quoted and not
re-measured here. The binding class states how the receipt relates to this run;
`source_bound_different_analyzed_input` means the same original take but a
different analyzed derivative, and `synthetic_bank_not_take` means generated
cases, never this recording.

```{r receipts}
#| results: asis
receipts <- table_of("receipts.csv")
if (!is.null(receipts)) {
  receipts$sha256 <- prefix(receipts$sha256)
  receipts$file <- NULL
}
show_table(receipts)
figures <- table_of("receipt_figures.csv")
if (!is.null(figures)) figures$pointer <- NULL
show_table(figures)
```

## 4. Timing candidates

Operator-declared tempo and the fitted recording pulse are separate evidence.
Subdivision alignment remains uncertain, particularly for rests, syncopation,
tuplets and merged attacks.

```{r timing}
#| results: asis
if (verified) {
  declared <- value_of(identity, "declared_tempo_bpm")
  fitted <- value_of(identity, "fitted_pulse_bpm")
  if (!is.na(declared) && nzchar(declared)) cat("Operator-declared approximate tempo:", declared, "BPM\n\n")
  if (!is.na(fitted) && nzchar(fitted)) cat("Fitted recording pulse (candidate):", fitted, "BPM\n\n")
}
```

```{r events-plot}
#| fig-width: 9
#| fig-height: 3.6
source("plots.R")
if (verified) {
  plot_bundle_events(bundle_dir)
} else {
  abstain_plot("Bundle not verified; no event values shown")
}
```

The plot uses decoded-audio-relative seconds. Click and guitar onset candidates
may overlap; detector bias and room propagation delay affect timing. A tempo
candidate is not an accepted beat grid. Missed or extra notes require an approved
expected-rhythm reference.

## 5. Review flags (detector hypotheses)

These are automatic review candidates, not confirmed performance issues. They are
kept separate from user-reported annotations, which appear in section 6.

```{r flags}
#| results: asis
flags <- table_of("review_flags.csv")
if (verified) {
  cat("Review flags in bundle:", value_of(identity, "review_flags_rows"), "of",
      value_of(identity, "review_flags_total"), "(row cap 200).\n\n")
}
if (!is.null(flags) && nrow(flags)) {
  counts <- as.data.frame(table(kind = flags$kind), stringsAsFactors = FALSE)
  names(counts) <- c("detector hypothesis kind", "rows")
  show_table(counts)
} else {
  cat("No source-bound review flags in this bundle.\n\n")
}
```

## 6. Corpus coverage: operator-labelled versus generated banks

The two pools are never summed. Absence of labels is not evidence of correctness.

```{r corpus}
#| results: asis
corpus <- table_of("corpus.csv")
if (!is.null(corpus)) {
  statement <- corpus$value[corpus$pool == "operator_labelled" & corpus$field == "statement"]
  if (length(statement)) cat("**", statement[1], "**\n\n", sep = "")
}
show_table(corpus)
annotations <- table_of("annotations.csv")
cat("User-reported annotations (structured fields only; free text is never copied):\n\n")
show_table(annotations, "No bound operator annotations.")
```

## 7. Unknowns

```{r unknowns}
#| results: asis
show_table(table_of("unknowns.csv"))
```

## 8. Listening review

Listening acceptance is not established. Record an operator review in a copy of
the all-null template `docs/spec/examples/listening-review.json`, bound to this
bundle's run and hashes. Compare at matched playback loudness. Listen for
low-string weight near the 32.7 Hz C1 fundamental, preserved pick attacks,
palm-mute articulation, saturated texture, sustain and natural tails. Inspect the
residual for removed musical detail. A mono-mixture residual is a diagnostic
estimate, not a recovered original stem. Open the run directory's plain
`report.html` for playback.
